---
title: "beginning_bayes"
output: html_document
---

# Beginning Bayes

## Bayesian Inference 

```{r message=FALSE, warning=FALSE}
library(TeachBayes)
```


```{r}
areas <- c(2,1,2,1,2)
spinner_plot(areas)
```
```{r}
spinner_probs(areas)
```

```{r}
df = data.frame(Region = 1:5, areas, Probability = areas/sum(areas))

df
```
```{r}
spins = spinner_data(areas, 1000)

bar_plot(spins)
```

```{r}
S = summarise(group_by(data.frame(Region=spins),Region), N=n())
S
```

Construct frequency table of spins:

```{r}
table(spins)
```

Find fraction of spins equal to 2:

```{r}
mean(spins==2 )
```

```{r}
bayes_df = data.frame(Model=paste("Spinner", c("A","B","C","D"))) 

bayes_df$Prior = rep(0.25,4)

bayes_df$Likelihood = round(c(1/3,1/2,1/4,1/6),2)

bayes_df = bayesian_crank(bayes_df)

bayes_df
```

```{r}
prior_post_plot(bayes_df)
```

## Binomial Probability


$$ Likelihood = \left(^{20}_{12} \right) p^{12} (1-p)^8  $$


```{r}

bin_df = data.frame(P = seq(0.3,0.8, by = 0.1), Weight = c(1,1,2,2,1,1), Prior=c(1,1,2,2,1,1)/8) 

bin_df$Likelihood = dbinom(12,size=20, prob = bin_df$P)

bin_df = bayesian_crank(bin_df)

round(bin_df, 3)
```

```{r}

prior_post_plot(bin_df)

```


Continous prior - beta curve

$$Prior = p^{a-1} (1-p)^{b-1}$$ 




```{r}
beta_area(0.4, 0.7, c(7,10))
```



```{r}
beta_quantile(0.25, c(7,10))
```

```{r}
p50 = list(x = 0.55, p = 0.5) #median 
p90 = list(x = 0.80, p = 0.9)
beta.select(p50, p90)
```


```{r}
beta_draw(beta.select(p50, p90))
```


```{r}
prior_par = c(4.7, 3.38)
data = c(12,8)
post_par = prior_par + data
```

Hypothesis testing: 

area is only 0.004 => regect > 0.95

```{r}
beta_area(0.95,1, beta.select(p50, p90))
```




Computing intervals:

90% interval

```{r}
beta_interval(0.9, beta.select(p50, p90))
```

bayesian intervals are shorter, as they combine info from prior and data


Posterior simulation:
```{r}
?rbeta

sim_p = rbeta(1000, 16.91, 11.38)

hist(sim_p, freq = F)
curve(dbeta(x, 16.91, 11.38), add=T, col="red", lwd=3)

```




```{r}

prob = sum(sim_p<0.5)/1000

prob
```


pbeta/qbeta - exact measurments

rbeta - difficult posteriors


```{r}
pbeta(0.5, 16.91, 11.38)
```

```{r}
qbeta(0.5, 16.91, 11.38)
```



```{r}
quantile(sim_p, c(0.05,0.95))
```


```{r}
sim_logit = log(sim_p/(1-sim_p))
hist(sim_logit, freq = F)
```



```{r}
quantile(sim_logit, c(0.1,0.9))
```


